
\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{fontawesome5}
\setlength{\parskip}{4pt}
\pagenumbering{gobble}
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{AMIT KUMAR BIND}} \\
    Bhagalpur, Bihar, India 813210 \\
    \faEnvelope\ \href{mailto:amit2.230101022@iiitbh.ac.in}{amit2.230101022@iiitbh.ac.in} \hspace{0.5cm} 
    \faPhone\ +91 7879097826 \hspace{0.5cm} 
    \faGithub\ \href{https://github.com/Akm1923}{github.com/Akm1923} \hspace{0.5cm} 
    \faLinkedin\ \href{https://linkedin.com/in/amit-kumar-bind}{linkedin.com/in/amit-kumar-bind}
\end{center}

\vspace{0.3cm}

\section*{PROFESSIONAL SUMMARY}
Results-driven Machine Learning Engineer and Data Scientist with 2+ years of hands-on experience in AI, Deep Learning, and Full-Stack Development. Expertise in Python, TensorFlow, PyTorch, and Computer Vision. Proven ability to develop end-to-end AI solutions, scalable systems, and impactful machine learning applications.

\section*{CORE COMPETENCIES}
\textbf{Programming:} Python, C++, C, SQL, JavaScript, HTML, CSS, R \quad
\textbf{ML \& AI:} Supervised, Unsupervised, Deep Learning, Computer Vision, NLP, Reinforcement Learning \\
\textbf{Frameworks:} TensorFlow, Keras, PyTorch, Scikit-learn, XGBoost, LightGBM, CatBoost \\
\textbf{Data Science:} NumPy, Pandas, Matplotlib, Seaborn, Statistical Modeling, Feature Engineering \\
\textbf{Deep Learning:} CNN, RNN, LSTM, GRU, Transformers, BERT, GPT, U-Net, ResNet, Attention \\
\textbf{Technologies:} OpenCV, LangChain, Hugging Face, MLOps, Model Deployment \\
\textbf{Web Development:} Flask, Streamlit, FastAPI, Frontend, Backend \\
\textbf{Database:} ChromaDB, SQL, NoSQL, MySQL, Vector Databases \\
\textbf{Cloud \& DevOps:} AWS, Docker, Git, CI/CD \\
\textbf{Specialized:} Image Processing, Object Detection, Segmentation, Web Scraping, ETL, A/B Testing \\
\textbf{BI \& Analytics:} Excel, Predictive Analytics, Time Series Analysis

\section*{PROFESSIONAL EXPERIENCE}
\textbf{Machine Learning Research Intern} \hfill \textit{May 2025 - July 2025} \\
Indian Institute of Technology Roorkee \\
\begin{itemize}[leftmargin=*]
    \item Applied Deep Learning to optimize hydrokinetic turbine efficiency with 15\% performance improvement.
    \item Built Data Science Pipeline with 95\% model accuracy for predictive renewable energy systems.
    \item Used TensorFlow, PyTorch, Python for supervised learning model development.
    \item Collaborated with 5-member research team on statistical analysis, computing, and reporting.
\end{itemize}

\section*{KEY PROJECTS}
\textbf{Real-Time Construction Monitoring with Computer Vision} \\
\textbf{Technologies:} Mask R-CNN, OpenCV, Python, Deep Learning \\
\begin{itemize}[leftmargin=*]
    \item Developed automated monitoring system with 99\% object detection accuracy.
    \item Integrated TOF sensors with CNN for real-time area measurement.
    \item Optimized deep learning model with 95\% precision on aerial image dataset.
    \item Reduced manual inspection time by 70\% using CI/CD pipeline.
\end{itemize}

\textbf{Enterprise RAG Chatbot with LLMs} \\
\textbf{Technologies:} LangChain, Groq API, Hugging Face, ChromaDB, Python \\
\begin{itemize}[leftmargin=*]
    \item Built Retrieval-Augmented Generation (RAG) chatbot processing 10,000+ documents.
    \item Integrated Groq API reducing response time by 90\% for LLM inference.
    \item Developed semantic search with BERT achieving 92\% similarity accuracy.
    \item Scaled to support 1000+ concurrent users with Vector Database.
\end{itemize}

\textbf{Medical Image Segmentation with Deep Learning} \\
\textbf{Technologies:} TensorFlow, Keras, U-Net, CNN, Python \\
\begin{itemize}[leftmargin=*]
    \item Achieved 96\% segmentation accuracy on biomedical images.
    \item Improved generalization by 25\% with data augmentation techniques.
    \item Applied Transfer Learning reducing training time by 40\%.
    \item Validated performance using IoU, Dice score, F1-score.
\end{itemize}

\textbf{Scalable Web Scraping and Analytics Platform} \\
\textbf{Technologies:} Python, BeautifulSoup, Pandas, ETL, Data Mining \\
\begin{itemize}[leftmargin=*]
    \item Scraped and analyzed 8000+ product reviews and startup datasets.
    \item Built scalable ETL pipeline achieving 98\% data quality score.
    \item Reduced scraping failure rate by 80\% with error handling and retries.
    \item Performed data cleaning, transformation, statistical analysis.
\end{itemize}

\newpage

\section*{EDUCATION}
\textbf{B.Tech, Computer Science and Engineering} \hfill \textit{Expected 2027} \\
Indian Institute of Information Technology Bhagalpur \\
\textbf{CGPA:} 7.75/10 \hfill 4th Semester \\
Relevant Coursework: DSA, Machine Learning, Deep Learning, OS, DBMS, CN, Software Engineering, Statistics

\textbf{Higher Secondary (12th), Excellent Circle of Studies} \hfill \textit{90.05\%} \\
Gwalior, Madhya Pradesh

\textbf{Secondary (10th), Excellent Circle of Studies} \hfill \textit{89.5\%} \\
Gwalior, Madhya Pradesh

\section*{ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
    \item National Finalist, Smart India Hackathon 2024 (Top 1.5\% of 86,000+ teams).
    \item CodeChef 2-Star Coder, Top 15\% globally, 200+ problems solved.
    \item Academic Excellence: Dean's List (2 semesters), 7.75 CGPA.
    \item Research Publication (under review) on AI for renewable energy.
    \item Led 3 project teams in hackathons and academic projects.
\end{itemize}

\section*{CERTIFICATIONS}
\begin{itemize}[leftmargin=*]
    \item Machine Learning \& Deep Learning Specialization — CampusX.
    \item Data Science \& Analytics — CampusX.
    \item Deep Learning Specialization — CampusX.
    \item Python for Data Science \& AI — Practical Projects.
    \item Git \& GitHub Professional — Version Control.
\end{itemize}

\section*{ADDITIONAL INFORMATION}
\begin{itemize}[leftmargin=*]
    \item Continuous Learning: Generative AI, LLMs, MLOps.
    \item Industry Awareness: AI, Data Science, Software Engineering trends.
\end{itemize}

\end{document}
